Vragenlijst thesis evaluatie

### 2015-04-17 doc/template/chap-5.tex
Latex werkt weer !!!

Two players, player X (blue) and player Y (red) attempt to maintain control over a shared resource.
At anytime in the game each player is allowed to play ‘flip’.
The only way a player can learn the state of the game (who is in control) is when they play 'flip’.
If a player is in control of the resource and they play 'flip’ they remain in control of the resource.
If a player is not in control of the resource and they play 'flip’ they gain control of the resource.
Players gain points for the length of time they control the resource.
Players lose points every time they play flip.
This reflects the situation that the CIA is placed in with regard to moles/enemy spies. They don't know if they have been compromised. They can perform an investigation and determine if they have been compromised, also catching the spy in the act, but this action is very expensive. That is, the CIA has to trade off between remaining''mole free'' (a good) and investigations (an expense).

>>>>

Two players, player X (blue) and player Y (red) attempt to maintain control over a shared resource.
At anytime in the game each player is allowed to play 'flip'.
The only way a player can learn the state of the game (who is in control) is when they play flip.
If a player is in control of the resource and they play flip they remain in control of the resource.
If a player is not in control of the resource and they play flip they gain control of the resource.
Players gain points for the length of time they control the resource.
Players lose points every time they play flip.
This reflects the situation that the CIA is placed in with regard to moles/enemy spies. They don't know if they have been compromised. They can perform an investigation and determine if they have been compromised, also catching the spy in the act, but this action is very expensive. That is, the CIA has to trade off between remaining''mole free'' (a good) and investigations (an expense).
